---
title: "assignment2"
output: github_document
date: "2023-08-24"
---
```{r}
library(raster)
library(habtools)
library(ggplot2)
library(dplyr)
library(fishualize)

plot(horseshoe)

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Current lab 
Dr.Hunter-advisor Hadfield Lab GA

Project focus 
Temperature tolerance of native vs. invasive oyster larvae in Pearl Harbor

Why you chose this course 
It sounds really interesting and I want to learn R. Also, most of my research experience has focused in on the small scale coral reef structure- looking at how and why invertebrate larvae settle when/where they do, so I think it will be really cool to look at structure/fuction on other levels. 

What do you want to learn about the most in this course
Similar to my previous answer, I think it will be really interesting to learn about the coral reef habitat from other perspectives. I am also excited to learn about new technologies for learning about the reefs.

Your R experience
none 

Fun fact 
One time I got stranded at a Yodeling Festival in Switzerland.

